Verifying Demonstrations

### 2019-02-27 paper/verifiability-analysis.tex
It's TF that's the relevant property for Alice's relay

Relaying the communication is \iac{DBDF} attack against the \ac{DB} protocol.
We assumed \ac{DBDF} resistance for the \ac{DB} protocol, so Alice cannot 
succeed with more than negligible probability.

>>>>

Relaying the communication is an attack against the \ac{DB} protocol.
We assumed \iac{DB} protocol with \ac{DBTF} resistance (the most relevant 
property for this situation), so Alice cannot succeed with more than negligible 
probability.
